Lessons learned: creating tutorials teaching Agent-Based Modelling for Archaeologists

### 2024-03-19 paper.Rmd
Update link
Credits Saxion students

The tutorials are publically hosted on GitHub ^[https://ABMArchaeologists.github.io/ABMA_Website/#/]. Anyone interested can download the tutorials and their source code. To increase the accessibility and visibility of the tutorials, a website has been launced^[https://ABMArchaeologists.github.io/ABMA_Website/#/]. On this website, the tutorials can be followed without the need to download any software.

Besides, the tutorial, the website provides: a link that can be used for feedback, basic explanations of agent-based modelling, an introductory presentation from one of the workshops, videos from an online course at Leiden University [@spoc2019] and external resources people can use to learn agent-based modelling.

@@

>>>>

The tutorials are publically hosted on GitHub^[https://github.com/ABMArchaeologists/ABMA_tutorials/]. Anyone interested can download the tutorials and their source code. To increase the accessibility and visibility of the tutorials, a website has been launced^[https://ABMArchaeologists.github.io/ABMA_Website/#/]. On this website, the tutorials can be followed without the need to download any software.

Besides, the tutorial, the website provides: a link that can be used for feedback, basic explanations of agent-based modelling, an introductory presentation from one of the workshops, videos from an online course at Leiden University [@spoc2019] and external resources people can use to learn agent-based modelling. The website was mainly developed by one of the student groups from Saxion University of Applied Sciences, see the acknowledgements.

@@

This last group, we want to thank for providing us with the website on which the tutorials are hosted.
